---
title: "Housing Burden & Opportunites for Affordable Housing in San Francisco"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r global, include=F}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(plotly)

sf_burden_pumas_plot <- readRDS("sf_burden_pumas_plot.rds")
sf_burden_cost_plot <- readRDS("sf_burden_cost_plot.rds")
unused_floors_plot <- readRDS("unused_floors_plot.rds")
add_units_allowed_plot <- readRDS("add_units_allowed_plot.rds")

```


Row
-------------------------------------
    
### Cost-Burdened Households with Children in San Francisco

This map shows the proportion of households with children that spend more than 30% of their income on housing costs by Public Use Micro Area (PUMA).  For more information on each of these maps, visit this [page](https://fis1995.github.io/francinestephens.github.io/A6_landuse_SF.html).

```{r}
sf_burden_pumas_plot %>% setView(-122.436057, 37.756865, zoom = 11)

```
   

### Total Housing Cost Burden   

Total housing cost burden reflects the total amount of the housing cost above the 30% threshold for all of those households combined within a given PUMA.

```{r}
sf_burden_cost_plot %>% setView(-122.436057, 37.756865, zoom = 11)

```


Row
-------------------------------------
   
### Underutilized Space in Bayview

This map shows the square footage of floor area that could be built within this targeted set of blocks in the Bayview neighborhood. These estimates were constructed at the parcel level using current zoning codes for San Francisco. 

```{r}
unused_floors_plot

```   
 
### Additional Units Allowed

If all of the underutilized space were to be used for housing, 172 more dwelling units could be built in this targeted set of blocks in Bayview without changing zoning.

```{r}
add_units_allowed_plot

```